Coevolution leaves a stronger imprint on interactions than on community structure

### 2017-05-23 manuscript/manuscript.Rmd
update the text with DBS comments

![Spatial distribution of co-phylogenetic matching across the 51 sites. For each location, we indicate whether or not the structure of regional and local interaction networks is consistent with phylogenetic congruence. Locations where the local network shows a significant co-phylogenetic structure are marked with triangles. Locaitions where the regional network shows a significant co-phylogenetic structure are in black. See also {@tbl:contingency}.](figure/maps-1.pdf){#fig:maps width=100%}

@@

The lack of a relationship between an interaction's probability of occurring (which represents
their ecological stability) and its contribution to the co-phylogenetic process
(which can be a proxy of their evolutionary stability) draws into question
the basic long-term stability of interactions. Specifically, the existence of
interactions with strong co-phylogenetic contribution, but low probability, is
puzzling. It is tempting to hypothesize that these interactions may have once been strong
enough to drive (co-)speciation, but are now decaying, due either to the fact
that the host-parasite pair has been disrupted or as a consequence of
ecological processes. DBS Can you spell this transition out for me better? I don't quite see the link. DBS @janz11err show that parasites can frequently acquire
hosts that are not closely related to their initial host. This phenomenon,
dubbed the "parasite paradox", can be responsible for a large number of
diversification events, as parasites will be introduced to a novel environment
when exposed to a novel host. The acquisition of novel hosts proceeds primarily
from ecological contact between distantly related species. This emphasizes the
need to account for the spatial structure of species interactions in these
studies -- because all species do not co-occur at all places, the potential for
ecological contact with novel hosts varies across space. Ideally, reconstruction
of the ancestral range of the species can shed some light on whether acquisition
of distantly related species happened, and where.

@@

Finally, we would like to acknowledge some limitations in the data.
Host-parasite evolution usually follows a number of canonical coevolutionary
scenarios [@page03ttp]: true cospeciation, where the two speciation events are
simultaneous; pseudo- or delayed-cospeciations, where one speciation event
happens after the other; host shift, where the parasite acquires a new host
(and can subsequently lose the previous host, undergo speciation, or maintain its
ability to use the previous host); and host-range expansion, in which the parasite
acquires a novel host.
DBS Are we sure the differences between host shift and host-range expansion clear enough in the above? DBS
When the likelihood of both host and parasite extinction
events are added to these models, the variety of outcomes is considerable.
@dev07wch shows that host-switch-like events can result in matching trees, and
so one could argue that the continental-level signal of tree matching can emerge
from numerous host-shift events [although the results of @kras12psm do not
support this scenario]. Because separating true cospeciation events from all
other situations is difficult without time-calibrated trees, @dev13cvh suggest
that the number of cospeciation events is inflated by cophenetic methods like
*PACo* or *ParaFit* [although @lope01mpf reported an increased number of
cospeciations when accounting for time of speciation events]. This reinforces
the need for high-quality phylogeny data calibrated for communities in which the
interactions are known. Not only will this help us make more robust inference about
the evolution of networks [@eklo16pcf], it will also help us leverage information about
species interactions embedded within networks to better understand coevolutionary
dynamics.

>>>>

![Spatial distribution of co-phylogenetic matching across the 51 sites. For each location, we indicate whether or not the structure of regional and local interaction networks is consistent with phylogenetic congruence. Locations where the local network shows a significant co-phylogenetic structure are marked with triangles. Locaitions where the regional network shows a significant co-phylogenetic structure are in black. See also {@tbl:contingency}. ](figure/maps-1.pdf){#fig:maps width=100%}

@@

The lack of a relationship between an interaction's probability of occurring
(which represents their ecological stability) and its contribution to the
co-phylogenetic process (which can be a proxy of their evolutionary stability)
draws into question the basic long-term stability of interactions. Specifically,
the existence of interactions with strong co-phylogenetic contribution, but low
probability, is puzzling. It is tempting to hypothesize that these interactions
may have once been strong enough to drive (co-)speciation, but are now decaying,
due either to the fact that the host-parasite pair has been disrupted (by
additional speciation and extinction events in the hosts or parasites) or as a
consequence of ecological processes (for example, changes in the environment
modifying the strength of some interactions). @janz11err show that parasites can
frequently acquire hosts that are not closely related to their initial host.
This phenomenon, dubbed the "parasite paradox", can be responsible for a large
number of diversification events, as parasites will be introduced to a novel
environment when exposed to a novel host. The acquisition of novel hosts
proceeds primarily from ecological contact between distantly related species.
This emphasizes the need to account for the spatial structure of species
interactions in these studies -- because all species do not co-occur at all
places, the potential for ecological contact with novel hosts varies across
space. Ideally, reconstruction of the ancestral range of the species can shed
some light on whether acquisition of distantly related species happened, and
where.

@@

Finally, we would like to acknowledge some limitations in the data.
Host-parasite evolution usually follows a number of canonical coevolutionary
scenarios [@page03ttp]: true cospeciation, where the two speciation events are
simultaneous; pseudo- or delayed-cospeciations, where one speciation event
happens after the other; host shift, where the parasite acquires a new host (and
can subsequently lose the previous host, or undergo speciation); and host-range
expansion, in which the parasite acquires a novel host and retains the ability
to infect the previous host. When the likelihood of both host and parasite
extinction events are added to these models, the variety of outcomes is
considerable. @dev07wch shows that host-switch-like events can result in
matching trees, and so one could argue that the continental-level signal of tree
matching can emerge from numerous host-shift events [although the results of
@kras12psm do not support this scenario]. Because separating true cospeciation
events from all other situations is difficult without time-calibrated trees,
@dev13cvh suggest that the number of cospeciation events is inflated by
cophenetic methods like *PACo* or *ParaFit* [although @lope01mpf reported an
increased number of cospeciations when accounting for time of speciation
events]. This reinforces the need for high-quality phylogeny data calibrated for
communities in which the interactions are known. Not only will this help us make
more robust inference about the evolution of networks [@eklo16pcf], it will also
help us leverage information about species interactions embedded within networks
to better understand coevolutionary dynamics.
